Timeliness of security updates for Android

### 2014-10-23 securityupdates.tex
Explain why we did not exploit devices

\section{Android Ecosystem}
\subsection{Running a version of Android known to be vulnerable makes a device vulnerable}
While we have not tried to exploit these vulnerabilities\todo{ethics} on the devices in order to test whether the devices are actually vulnerable, we are confident that most devices will be if they are running a vesion known to be vulnerable. \todo{WHY?}

>>>>

\section{Android Ecosystem}
\subsection{Running a version of Android known to be vulnerable makes a device vulnerable}
We have not tried to exploit these vulnerabilities on the devices in order to test whether the devices are actually vulnerable.
Doing so would be difficult both ethically, as it would pose a high risk to user devices and mean that our code could easily be maliciously repurposed, and practically as getting all the exploits working reliably on all the devices they could be made to work reliably on requires extensive testing.
We are confident that most devices will be vulnerable if they are running a version of Android known to be vulnerable. \todo{WHY?}
